The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2009-12-20 script/de/chapters/authors.tex
CT Script: Update to Sneakers (according to HW)

% Gefunden in: CRYPTO-GRAM, January 15, 2007, by Bruce Schneier
\item[\textrm{[Kipling1901]}] \index{Kipling 1901}
    Rudyard Kipling\index{Kipling, Rudyard}, \\
    {\em Kim}, 1901. \\
    Dieser Roman wird in der Besprechung von Rob Slade%
    \footnote{See
          \href{http://catless.ncl.ac.uk/Risks/24.49.html\#subj12} %% \ vor # nötig !
       {\texttt{http://catless.ncl.ac.uk/Risks/24.49.html\#subj12}}.
    }
    folgendermaßen beschrieben:
    "`Kipling packte viele Informationen und Konzepte in seine Geschichten.
    In "`Kim"' geht es um das große "`Spiel"' Spionage und Bespitzelung.
    Schon auf den ersten 20 Seite finden sich Authentisierung über Besitz,
    Denial of Service, Sich-für-jemand-anderen-Ausgeben (Impersonation),
    Heimlichkeit, Maskerade, Rollen-basierte Autorisierung (mit 
    Ad-hoc-Authentisierung durch Wissen), Abhören, und Vertrauen basierend
    auf Datenintegrität.
    Später kommen noch Contingency Planning gegen Diebstahl und
    Kryptographie mit Schlüsselwechsel hinzu."'\\
    Das Copyright des Buches ist abgelaufen%
    \footnote{Sie können es lesen unter:\\
          \href{http://whitewolf.newcastle.edu.au/words/authors/K/KiplingRudyard/prose/Kim/index.html}
       {\texttt{http://whitewolf.newcastle.edu.au/words/authors/K/KiplingRudyard/prose/Kim/index.html}},\\
          \href{http://kipling.thefreelibrary.com/Kim}
       {\texttt{http://kipling.thefreelibrary.com/Kim}} or\\
          \href{http://www.readprint.com/work-935/Rudyard-Kipling}
       {\texttt{http://www.readprint.com/work-935/Rudyard-Kipling}}.
    }.\\

@@

\item[\textrm{[Robinson1992]}] \index{Robinson 1992}
    Regie Phil Alden Robinson, \\
    {\em Sneakers - Die Lautlosen (Orginaltitel: Sneakers)},
    Universal Pictures Film, 1992. \\
    In diesem Film versuchen die "`Sneakers"', Computerfreaks um ihren Boss
    Martin Bishop, den "`Bösen"' das Dechiffrierungsprogramm SETEC abzujagen.
    SETEC wurde von einem genialen Mathematiker vor seinem gewaltsamen Tod
    erfunden und kann alle Geheimcodes dieser Welt entschlüsseln.\\
    Das Verfahren wird nicht beschrieben.\\

>>>>

% Gefunden in: CRYPTO-GRAM, January 15, 2007, by Bruce Schneier
\item[\textrm{[Kipling1901]}] \index{Kipling 1901}
    Rudyard Kipling\index{Kipling, Rudyard}, \\
    {\em Kim}, 1901. \\
    Dieser Roman wird in der Besprechung von Rob Slade%
    \footnote{Siehe
      # \href{http://catless.ncl.ac.uk/Risks/24.49.html\#subj12} %% \ vor # nötig !
        \url{http://catless.ncl.ac.uk/Risks/24.49.html\#subj12}.
    }
    folgendermaßen beschrieben:
    "`Kipling packte viele Informationen und Konzepte in seine Geschichten.
    In "`Kim"' geht es um das große "`Spiel"' Spionage und Bespitzelung.
    Schon auf den ersten 20 Seite finden sich Authentisierung über Besitz,
    Denial of Service, Sich-für-jemand-anderen-Ausgeben (Impersonation),
    Heimlichkeit, Maskerade, Rollen-basierte Autorisierung (mit 
    Ad-hoc-Authentisierung durch Wissen), Abhören, und Vertrauen basierend
    auf Datenintegrität.
    Später kommen noch Contingency Planning gegen Diebstahl und
    Kryptographie mit Schlüsselwechsel hinzu."'\\
    Das Copyright des Buches ist abgelaufen%
    \footnote{Sie können es lesen unter:\\
          \url{http://whitewolf.newcastle.edu.au/words/authors/K/KiplingRudyard/prose/Kim/index.html},\\
          \url{http://kipling.thefreelibrary.com/Kim} oder\\
          \url{http://www.readprint.com/work-935/Rudyard-Kipling}.
    }.\\

@@

\item[\textrm{[Robinson1992]}] \index{Robinson 1992}
    Regie Phil Alden Robinson, \\
    {\em Sneakers - Die Lautlosen (Orginaltitel: Sneakers)},
    Universal Pictures Film, 1992. \\
    In diesem Film versuchen die "`Sneakers"', Computerfreaks um ihren Boss
    Martin Bishop, den "`Bösen"' das Dechiffrierungsprogramm SETEC abzujagen.
    SETEC wurde von einem genialen Mathematiker vor seinem gewaltsamen Tod
    erfunden und kann alle Geheimcodes dieser Welt entschlüsseln.\\
    In dem Film wird das Verfahren nicht beschrieben%
    \footnote{
       An dem Film hatte Leonard Adleman (das "A" von RSA) als mathematischer
       Berater mitgearbeitet. Die recht lustige Geschichte über seine Mitwirkung
       bei Sneakers beschreibt er selbst auf seiner Homepage unter
       \url{http://www.usc.edu/dept/molecular-science/fm-sneakers.htm}.
       Man kann man davon ausgehen, dass es sich bei dem überall benutzten
       Verschlüsselungsverfahren um RSA handelt.      
       In dem Chip ist demnach ein bis dahin unbekanntes, schnelles 
       Faktorisierungsverfahren\index{Faktorisierung} implementiert.
    }
    .\\

### 2009-12-20 script/en/chapters/authors.tex
CT Script: Update to Sneakers (according to HW)

\item[\textrm{[Kipling1901]}] \index{Kipling 1901}
    Rudyard Kipling\index{Kipling, Rudyard}, \\
    {\em Kim}, 1901. \\
    Rob Slade's review%
    \footnote{See
          \href{http://catless.ncl.ac.uk/Risks/24.49.html\#subj12}
       {\texttt{http://catless.ncl.ac.uk/Risks/24.49.html\#subj12}}.
    }
    of this novel says:
    ``Kipling packed a great deal of information and concept into his stories,
    and in ``Kim'' we find The Great Game: espionage and spying.  Within the
    first twenty pages we have authentication by something you have, denial
    of service, impersonation, stealth, masquerade, role-based
    authorization (with ad hoc authentication by something you know),
    eavesdropping, and trust based on data integrity.  Later on we get
    contingency planning against theft and cryptography with key changes.''\\
    The book is out of copyright%
    \footnote{You can read it at:\\
          \href{http://whitewolf.newcastle.edu.au/words/authors/K/KiplingRudyard/prose/Kim/index.html}
       {\texttt{http://whitewolf.newcastle.edu.au/words/authors/K/KiplingRudyard/prose/Kim/index.html}},\\
          \href{http://kipling.thefreelibrary.com/Kim}
       {\texttt{http://kipling.thefreelibrary.com/Kim}} or\\
          \href{http://www.readprint.com/work-935/Rudyard-Kipling}
       {\texttt{http://www.readprint.com/work-935/Rudyard-Kipling}}.
    }.\\

@@

\item[\textrm{[Robinson1992]}] \index{Robinson 1992}
    Directed by Phil Alden Robinson, \\
    {\em Sneakers}, Universal Pictures Film, 1992. \\
    In this movie the ``sneakers'', computer experts under their boss Martin
    Bishop, try to get back the deciphering box SETEC from the ``bad guys''.
    SETEC, invented by a genius mathematician before he was killed, allows to
    decrypt all codes from any nation. \\
    The code is not described in any way.\\

>>>>

\item[\textrm{[Kipling1901]}] \index{Kipling 1901}
    Rudyard Kipling\index{Kipling, Rudyard}, \\
    {\em Kim}, 1901. \\
    Rob Slade's review%
    \footnote{See
        \url{http://catless.ncl.ac.uk/Risks/24.49.html\#subj12}.
    }
    of this novel says:
    ``Kipling packed a great deal of information and concept into his stories,
    and in ``Kim'' we find The Great Game: espionage and spying.  Within the
    first twenty pages we have authentication by something you have, denial
    of service, impersonation, stealth, masquerade, role-based
    authorization (with ad hoc authentication by something you know),
    eavesdropping, and trust based on data integrity.  Later on we get
    contingency planning against theft and cryptography with key changes.''\\
    The book is out of copyright%
    \footnote{You can read it at:\\
          \url{http://whitewolf.newcastle.edu.au/words/authors/K/KiplingRudyard/prose/Kim/index.html},\\
          \url{http://kipling.thefreelibrary.com/Kim} or\\
          \url{http://www.readprint.com/work-935/Rudyard-Kipling}.
    }.\\

@@

\item[\textrm{[Robinson1992]}] \index{Robinson 1992}
    Directed by Phil Alden Robinson, \\
    {\em Sneakers}, Universal Pictures Film, 1992. \\
    In this movie the ``sneakers'', computer experts under their boss Martin
    Bishop, try to get back the deciphering box SETEC from the ``bad guys''.
    SETEC, invented by a genius mathematician before he was killed, allows to
    decrypt all codes from any nation. \\
    In the movie the code is not described in any way%
    \footnote{
       Leonard Adleman (the "A" within RSA) worked as mathematical consultant
       for ``Sneakers''. He describes the funny story about his contribution
       at his homepage 
       \url{http://www.usc.edu/dept/molecular-science/fm-sneakers.htm}.
       It is assumed that the cipher used everywhere is RSA.      
       According to that within the chip a fast, unknown factorization
       method\index{Factorization} is implemented.
    }
    .\\
